\Title

### 2016-08-17 manuscript/manuscript.tex
Make CV plots pcolor instead of contourf
Fixes #33

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}) in $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:crust1-data}a)
        and the estimated depths.
        (e) Histogram of the inversion residuals
        (observed minus predicted data).
        (f) Histogram of the differences between
        the synthetic seismic observations (Fig.~\ref{fig:crust1-data}c)
        and the estimated depths.
        (g) The inversion residuals.
        (h) Difference between the seismic and the estimated depths.
    }
    \label{fig:crust1-results}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Cross-validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colored contours represent
        the Mean Square Error (Eq.~\ref{eq:msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:sam-cv}
\end{figure}

@@

We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
inversions.
We test all combinations of
seven values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
with 50 $kg/m^3$ intervals.
Fig.~\ref{fig:sam-cv}b shows a map of the MSE
with respect to the \citet{assumpcao2013a} data set.
The MSE has a well-defined minimum, indicated by the red triangle,
at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/synthetic-crust1-results}
    \caption{
        Inversion results from the CRUST1.0 synthetic data.
        (a) Cross-validation curve used to determine
        the regularization parameter (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}) is found at
        $\mu = 0.0001$ (red triangle).
        (b) Cross-validation results used to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}) in
        $km^2$.
        The minimum (red triangle) is found at $z_{ref} = 30\ km$
        and $\Delta\rho = 350\ kg/m^3$.
        (c) The estimated Moho depth.
        (d) Difference between the CRUST1.0 model depths
        (Fig.~\ref{fig:crust1-data}a)
        and the estimated depths.
        (e) Histogram of the inversion residuals
        (observed minus predicted data).
        (f) Histogram of the differences between
        the synthetic seismic observations (Fig.~\ref{fig:crust1-data}c)
        and the estimated depths.
        (g) The inversion residuals.
        (h) Difference between the seismic and the estimated depths.
    }
    \label{fig:crust1-results}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\columnwidth]{figures/south-america-cv}
    \caption{
        Cross-validation results for the South American Moho inversion.
        (a) Cross-validation to determine the regularization parameter $\mu$
        (Eq.~\ref{eq:goalfunction}).
        The minimum Mean Square Error (Eq.~\ref{eq:msemu}),
        shown as a red triangle,
        corresponds to $\mu = 10^{-10}$.
        (b) Cross-validation to determine
        the reference level ($z_{ref}$) and the density-contrast ($\Delta\rho$).
        The colors represent the Mean Square Error (Eq.~\ref{eq:msehyper}).
        The minimum (red triangle) is found at $z_{ref} = 35\ km$
        and $\Delta\rho = 400\ kg/m^3$.
    }
    \label{fig:sam-cv}
\end{figure}

@@

We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
inversions.
We test all combinations of
seven values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
with 50 $kg/m^3$ intervals.
Fig.~\ref{fig:sam-cv}b shows a map of the MSE
with respect to the \citet{assumpcao2013a} data set.
The MSE has a minimum, indicated by the red triangle,
at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.
The minimum is not as well-defined as for the CRUST1.0 synthetic
(Fig.~\ref{fig:crust1-results}b),
which is expected because $\Delta\rho$ is not homogeneous across all of
South America and the surrounding oceans.
